\documentclass[a4paper]{article}
\usepackage{anyfontsize}
\usepackage{comment}
\usepackage{graphicx,subfigure,float}
\title{Statement of Research Interests} % Experience and 
\author{Abdennacer Hamdi\\
GSI Helmholtz Center\\
\texttt{a.hamdi@gsi.de}}
% \texttt{nacer@jlab.org}}
\date{\today}
\pagenumbering{gobble}

%\setlength{\topmargin}{-10mm}
%\setlength{\textwidth}{7in}
%\setlength{\oddsidemargin}{-8mm}
%\setlength{\textheight}{9in}
%\setlength{\footskip}{1in}
\usepackage[scale=0.88]{geometry}

\begin{document}
\fontsize{12}{15}
\selectfont
\maketitle

% \section*{Research and Teaching Experience}

~\par Since my early school years, I decided to specialize in nuclear physics and it turned out to be a successful decision. I graduated in 2010, and got a job at the Algiers Nuclear Research Center in Algeria, where I had next to my laboratory activities of evaluating and assessing environmental radioactivity, the opportunity to mentor master students in their manipulation of the Gamma spectroscopy detectors during different stages of calibration and manipulations, and offer them basic courses about Radiation protection.

~\par It was my pure and deep interest to understand the fundamental building blocks of matter and their interactions that led me towards particle physics. I followed a master degree program at the Clermont Auvergne University in France, and successfully graduated in June 2015. During my master degree, I was involved in two research projects. The first one was related to the search for a dark matter candidate in events with a single top quark and a missing transverse energy in the final state, the Monotop process, with the ATLAS experiment, and I studied the possibilities of extracting this signature from many background sources. The second one was dedicated to  the study of potential precision measurement of the Higgs boson and top quark coupling in the future $e^+e^-$ colliders, facing the challenges of a multi-jet final state while analyzing the $t\bar{t}H$ signature. I also studied the performance of a hadronic calorimeter proposed by the CALICE collaboration for the future leptonic colliders, where I had the opportunity to participate in taking data at CERN to study the calorimeter prototype. I studied its energy resolution using $\pi^{\pm}$ from test beam, and build a Monte Carlo simulation to demonstrate the possibility of separating particles of the jet in the calorimeter by their time of flight in the detector.

~\par After receiving some courses on hadron physics, I become very interested in the confinement of quarks and gluons inside QCD bound states, and about the predictions from theoretical models and lattice QCD calculations about the possibility of the existence of new exotic matter, due to the gluonic degrees of freedom, like glueballs and hybrids. While looking for a PhD project in that respect, I identified the PANDA experiment planned at FAIR to be a good opportunity to do these kind of investigations. As we joined the GlueX collaboration, I had the opportunity to work mainly and represent my analysis team in GlueX. After adapting to the new software environment and analysis methods of the experiment, I studied the $K^{+}K^{-}\pi^{+}\pi^{-}p$ channel, both in simulation and data, in the pursuit of a candidate for hybrid mesons, the $Y(2175)$. I successfully made a first measurement of the photoproduction cross section to two non-resonant sub channels. Due to lack of a good pion and kaon separation in the absence of the Cerenkov detector, I had to develop efficient analysis methods to overcome the challenging background. As a good discriminator between protons and pions was the energy loss in the Central Drift Chamber detector. I delivered the optimal mean truncation, for a better $dE/dx$ estimation, and the results are implemented in the current GlueX reconstruction software.
% \newpage
% All these challenges have strengthened my skills in scientific research and I have gained experience working with different research teams.

%\begin{comment}
% \section*{Research Interests}
% ~\par Modern physics experiments are a complicated synthesis of the theory behind an experiment, design and development of the detector to conduct the experiment, monitoring every detail of the extremely complicated detector, and analyzing the obtained data.\\
\newpage
~\par My research interests revolve around, exploring the nature of elementary particles, especially testing the predictions of the Standard and new models, and their interplay with astrophysics and cosmology. In that respect, the analysis of the XENON data, will open a great opportunity to search for potential candidates for DM, while overcoming the challenging background environment. I am confident that I can contribute to the efforts of the team in the physics analysis.
%Furthermore, studying the $e^+e^-$ processes will lead to make potential precision measurements and opportunities to search for New Physics
%as well as studying the properties of neutrinos while overcoming the large background environment. I am confident that I can contribute to the efforts of the team in the physics analysis.
%In that respect, the analysis of the Minerva high precision neutrino data, will open a great opportunity to study the neutrino oscillation parameters in depth, and the properties of neutrino and nuclei interactions. This will also shed some light on our understanding of high energy cosmic neutrinos.
% In that respect, the analysis of the IceCube Neutrino Observatory data, will open a great opportunity to study the origin of the high-energy neutrino signal, and its implication in our understanding of high energy cosmic rays.
% In that respect, the analysis of ALICE data will provide insights into the quarkonium photoproduction, and an exciting challenge to overcome the overlapping resonances with the charmonium state.
%the analysis of existing and future Gluex data will open a great opportunely to search for exotic meson candidates. Furthermore, the new installation of the DIRC detector at GlueX, will improve the PID, and eventually strengthening the exotic program.
%testing the predictions of the Standard Model, such as investigating both properties and dynamics governing their interactions, and test their impact on predictions from New Physics models. In that respect, the analysis of the ATLAS data, will open a great opportunely to probe the top-quark mass with a higher precision.\\
%  and their interplay with astrophysics and cosmology. particularly investigating the high energy cosmic neutrinos, and probing the hadronic processes in cosmic accelerators. In that respect, the analysis of the IceCube Neutrino Observatory data, will open a great opportunity to compare neutrino, cosmic rays and gamma ray fluxes, which will provide an excellent conditions for multi-messenger studies. I am confident that I can contribute to the efforts of the team in the physics analysis.

% In that respect, the analysis of the ATLAS data, will open a great opportunely to probe the top-quark mass with a higher precision. 
% In that respect, the analysis of current and upcoming high luminosity GlueX data, with the Detection of Internally Reflected Cherenkov light detector (DIRC) installation, will open a broader programme to map the spectrum of hadrons. I am confident that I can contribute to the efforts of the team in the physics analysis, particularly studying the $\gamma p \rightarrow \eta' \pi^{0} p$ reaction and perform a moment analysis to compare to the recent theoretical models including resonance in S, P or D waves for the $\eta \pi^{0} p$ final state (Phys. Rev. D 100, 054017).

% In one hand, mapping the baryon spectrum, in particular the cascades will provide more insights into the doubly-strange hyperons. On the other hand it is a great opportunity to detect and further analyse the $\phi\pi^{+}\pi^{-}$ channel, with all its rich potential. Both the $Y(2175)$ and the $\Xi$ are strange rich final states, and having the DIRC installed will improve $K/\pi$ separation power up to $4 GeV/c$.

Due to my experience regarding particle identification and hardware, I see also a potential to contribute to the efforts of the team addressing the needs of the experiment by developing the new software and hardware, in particular participating in the development and calibration of the photosensor detectors.

%for future direct detection experiments including directional dark matter experiments such as CYGNUS; and the dark matter detection aspects of the ATLAS experimental program at CERN.
% the new upgrade for the IceCube detector.
% in particular participating in the preparations for the upcoming HL-LHC, with the construction of the new ATLAS pixel detector.
~\par All these challenges have strengthened my skills in scientific research and I have gained experience working with different research teams. Being involved in many different experiments have laid a solid ground for me to further pursue an academic career. My ambition is to be a part of the processes that would lead us to a better understanding of matter in the universe.
%\end{comment}

\end{document}