\documentclass[11pt]{letter}
 \usepackage[utf8]{inputenc} % un package
 \usepackage[T1]{fontenc} % un second package
%\usepackage[latin1]{inputenc}
 \usepackage[english]{babel} % un troisième package
 \usepackage{textcomp}
 \usepackage{ifpdf}
\ifpdf
 \usepackage[pdftex]{graphicx}
 \else
 \usepackage[dvips]{graphicx}\fi
\pagestyle{empty}
\usepackage[scale=0.86]{geometry}
 \setlength{\parindent}{1em}
\addtolength{\parskip}{0.5pt}
\renewcommand{\ttdefault}{pcr}
 \begin{document}
 \sffamily
 \hfill
 %start
 \begin{flushleft}
 {\bfseries Abdennacer HAMDI}\\[.35ex]
 \small\itshape
 Résidence des Cézeaux, Rue Roche Genès\\
 63173 AUBIERE, France\\[.35ex]
 +33 615 787834\\
 hamdi.abdennacer@gmail.com
 \end{flushleft}
 %
 \begin{flushleft}
 To {\bfseries Prof. Dr. Guido Drexlin \\ Karlsruhe School of Elementary Particle and Astroparticle Physics, Science and Technology (KSETA )}\\[.35ex]
 \small\itshape
 Managing Office KSETA \\
Hermann-v.Helmholtz-Platz 1 \\
D-76344 Eggenstein-Leopoldshafen

 \end{flushleft}
 %
 \hfill
 %
 \begin{flushleft}
 Clermont-Ferrand, \today \\
 
 \end{flushleft}
 %
\textit{Subject:}  Application for PhD programme\\
\par Dear Prof. Dr. Guido Drexlin, 
%Content of the letter
~\par It is with great pleasure that I am writing to you to express my interest in applying for the PhD programme related  related to the Dark energy and TeV-scale physics. This programme appeals to me because of my strong interest in Particle Physics in addition to using the knowledge I’ve gained through my science classes in the university.
~\par I have been seeking just such an opportunity as this, it is clear to me that the Karlsruhe School of Elementary Particle and Astroparticle Physics, Science and Technology (KSETA ) is genuinely devoted to the advancement of knowledge and education of students, I will have the opportunity to learn from the best and the privilege to work in an international environment. I believe I can contribute to that mission through my passion for physics, my education and background would be a good match for your requirements.
~\par I mention that I am currently finishing my Master's degree in Particle Physics at the Blaise Pascal University in France. During this programme, I did two internships, one was with the ATLAS team on a subject looking for a candidate to the Dark Mater in a signature called $Monotop$ predicted by BSM theories, and a second with CALICE team on subject studying the Yukawa coupling of the $Higgs$ to the $top$ quark in $e^{+}e^{-}$ experiments, with a performance study of the new hadronic calorimeter proposed by the CALICE collaboration. I have worked as an Engineer Physicist specialized in Radiation Protection at the Algiers Nuclear Research Center. Graduated in year 2010, from Setif University in Algeria and got a Master degree in Nuclear Physics, completed with a Master thesis at the Draria Nuclear Research Center. All these challenges have strengthened my skills in laboratory work and I have gained experience working with different research teams.
~\par I am eager to talk with you about the research topic you proposed this would offer me the possibility of receiving the complete picture of this field.  I am interested in exploring the theoretical and experimental nature of elementary particles, especially grand unification theories and physics beyond the standard model, such as Supersymmetry and dark matter phenomenology. After completing this PhD programme, I plan to apply for research positions in the field of Particle Physics.
~\par I thank you for the opportunity to submit this application for your consideration. Please contact me if there is anything else I need to provide. I look forward to communicating with you in the near future.\\  % theoretical and, especially grand unification theories and physics beyond the standard model, particularly its signatures in colliders such as Supersymmetry and dark matter candidates experiments
%Please find enclosed my CV. \\ \\
Yours sincerely,

\begin{flushleft}
 {\bfseries Abdennacer HAMDI}
 \end{flushleft}
 \vfill
 \end{document}