\documentclass[11pt]{letter}
 \usepackage[utf8]{inputenc} % un package
 \usepackage[T1]{fontenc} % un second package
%\usepackage[latin1]{inputenc}
 \usepackage[english]{babel} % un troisième package
 \usepackage{textcomp}
 \usepackage{ifpdf}
\ifpdf
 \usepackage[pdftex]{graphicx}
 \else
 \usepackage[dvips]{graphicx}\fi
\pagestyle{empty}
\usepackage[scale=0.88]{geometry}
 \setlength{\parindent}{1em}
\addtolength{\parskip}{0.5pt}
\renewcommand{\ttdefault}{pcr}
 \begin{document}
 \sffamily
 \hfill
 %start
 \begin{flushleft}
 {\bfseries Abdennacer Hamdi}\\[.35ex]
 \small\itshape
 GSI Helmholtzzentrum f\"ur Schwerionenforschung GmbH\\
 Heckb\"uro 1.001, Planckstraße 1, 64291 Darmstadt, Germany\\[.35ex]
 +49 (0) 1781043207\\
 a.hamdi@gsi.de
 \end{flushleft}
 %
 \begin{flushleft}
 To {\bfseries Prof. Volker Crede}\\[.35ex]
 \small\itshape
 Florida State University \\
 Department of Physics \\
 206 Keen Building \\
 Tallahassee, FL  32306  USA

 \end{flushleft}
 %
 \hfill
 %
 \begin{flushleft}
 Darmstadt, \today \\
 
 \end{flushleft}
 %
\textit{Subject:} Application for postdoctoral position in experimental hadronic nuclear physics.\\
\par Dear Prof. Volker Crede, 
%Content of the letter
~\par It is with great pleasure that I am writing to you to express my interest in applying for the postdoctoral position in experimental hadronic nuclear physics to work together with the The Hadronic Nuclear Physics Group at the Florida State University. This project appeals to me because of my strong interest in hadron spectroscopy and particle physics in addition to using the knowledge I’ve gained through graduate research and my education in the university. I have been seeking just such an opportunity as this, it is clear to me that the Florida State University is genuinely devoted to the advancement of knowledge and education of students, I will have the opportunity to work and learn from the best and the privilege to work in an international environment. I believe I can contribute to that mission through my passion for physics, my education and background would be a good match for your requirements.
~\par I mention that I am currently finishing my Ph.D project at the Goethe University of Frankfurt, where i work on hadron spectroscopy, my goal is to search for a hybrid candidate with the GlueX experiment. I have a master's degree in particle physics at the Blaise Pascal University in France. During this programme, I did two internships, one was with the ATLAS team on a subject looking for a candidate to the Dark Mater in a signature called Monotop predicted by BSM theories, and a second with CALICE team on subject studying the Yukawa coupling of the Higgs to the top quark in $e^{+}e^{-}$ experiments, with a performance study of the new hadronic calorimeter proposed by the CALICE collaboration. I have worked as an Engineer Physicist specialized in Radiation Protection at the Algiers Nuclear Research Center, where i had the opportunity to teach master students about radiation protection and guide them through laboratory practical manipulations. Graduated in year 2010, from Setif University in Algeria and got a Master degree in Nuclear Physics, completed with a Master thesis at the Draria Nuclear Research Center. All these challenges have strengthened my skills in laboratory work and I have gained experience working with different research teams.
~\par I am eager to talk with you about the research project you proposed this would offer me the possibility of receiving the complete picture of this postdoctoral position. I am interested in exploring the nature of exotic hadrons at Gluex, especially with the recent installation of the DIRC detector and the high luminosty runs, this will open a broader programme to map these states. 
% I am interested in exploring the experimental nature of elementary particles, especially hadron spectroscopy, . 
%  grand unification theories and physics beyond the standard model, such as Supersymmetry and dark matter phenomenology. After completing this PhD programme, I plan to apply for research positions in the field of Particle Physics.
~\par I thank you for the opportunity to submit this application for your consideration. Please contact me if there is anything else I need to provide. I look forward to hearing from you in the near future.\\ \\ % theoretical and, especially grand unification theories and physics beyond the standard model, particularly its signatures in colliders such as Supersymmetry and dark matter candidates experiments
%Please find enclosed my CV. \\ \\
Yours sincerely,

\begin{flushleft}
 {\bfseries Abdennacer Hamdi}
 \end{flushleft}
 \vfill
 \end{document}