\documentclass[a4paper,roman]{article}
\usepackage{anyfontsize}
\usepackage{graphicx,subfigure,float}
\title{Statement of Research Experience and Interests}
\author{Abdennacer Hamdi\\
Goethe University of Frankfurt\\
\texttt{nacer@jlab.org}}
\date{\today}
\pagenumbering{gobble}

%\setlength{\topmargin}{-10mm}
%\setlength{\textwidth}{7in}
%\setlength{\oddsidemargin}{-8mm}
%\setlength{\textheight}{9in}
%\setlength{\footskip}{1in}
\usepackage[scale=0.88]{geometry}

\begin{document}
\fontsize{12}{15}
\selectfont
\maketitle

\section*{Research and Teaching Experience}
~\par At some point during my early school years, I decided to specialize in nuclear physics and it turned out to be a successful decision. I graduated in 2010, and got a job at the Algiers Nuclear Research Center (Algeria), where i had next to my laboratory activities of evaluating and assessing environmental radioactivity, the opportunity to mentor master students in their manipulation of the Gamma spectroscopy detectors during different stages of calibration and manipulations, and offer them basic courses about Radiation protection.

~\par It was my pure and deep interest to understand the fundamental building blocks of matter and their interactions that led me towards particle physics. I followed a master degree programme at the University of Blaise Pascal in France, and successfully graduated in June 2015. During my master degree, i did two research trainings. The first one was related to the search for a dark matter candidate in events with a single top quark and a missing transverse energy in the final state, Monotop process, with the ATLAS experiment, and i studied the possibilities of extracting this signature from many background sources. The second one was with the $e^+e^-$ team on the study of Yukawa coupling of the Higgs boson to the top quark in $e^+e^-$ experiments, and overcoming the challenges of a multi-jet final state while analyzing the $t\bar{t}H$ signature. I also studied the performance of a hadronic calorimeter proposed by the CALICE collaboration for the future leptonic colliders, where i had the opportunity to participate in taking data at CERN to study the calorimeter prototype. I studied its energy resolution using $\pi^{\pm}$ from test beam at CERN and build a Monte Carlo simulation to demonstrate the possibility of separating particles of the jet in the calorimeter by their time of flight in the detector.

~\par After receiving some courses on hadron physics, I was very interested in the confinement of quarks and gluons inside QCD bound states, and about the predictions from theoretical models and lattice QCD calculations about the possibility of the existence of new exotic matter, due to the gluonic degrees of freedom, like glueballs and hybrids. While looking for a PhD project in that respect, I identified the PANDA experiment planned at FAIR to be a good opportunity to do these kind of investigations. As we joined the GlueX collaboration, I had the opportunity to work mainly and represent my analysis team in the GlueX experiment. After adapting to the new software environment and analysis methods of the experiment, i studied the $\phi\pi^{+}\pi^{-}p$ channel, both in simulation and data, in the pursuit of a candidate for hybrid mesons, the $Y(2175)$. Due to lack of a good $\pi/K$ separation in the absence of the Cerenkov detector (DIRC), i had to develop efficient analysis methods to overcome the background. As a good discriminator between protons and pions was the energy loss in the Central Drift Chamber detector (CDC). I delivered the optimal mean truncation, for a better $dE/dx$ estimation, and the results are implemented in the current GlueX reconstruction software. I have been seeking just such an opportunity as this, it is clear to me that the The Helmholtz Graduate School for Hadron and Ion Research and Frankfurt University are genuinely devoted to the advancement of knowledge and education of students, I will have the opportunity to learn from the best and the privilege to work in an international environment. I believe I can contribute to that mission through my passion for physics. My education and background would be a good match for your requirements.\\
All these challenges have strengthened my skills in laboratory work and I have gained experience working with different research teams.

\section*{Research Interests}
~\par Modern high energy physics experiments are a complicated synthesis of the theory behind an experiment, design and development of the detector to conduct the experiment, monitoring every detail of the extremely complicated detector, and analyzing the obtained data.\\
My research interests revolve around, exploring the experimental nature of elementary particles, especially testing the predictions of the Standard Model, such as investigating both the dynamics governing the interaction of fundamental particles and the existence of new forms of matter, by spectroscopy experiments.\\
In that respect, the analysis of current and upcoming high luminosity GlueX data, with the Detection of Internally Reflected Cherenkov light detector (DIRC) installation, will open a broader programme to map the spectrum of hadrons. In one hand is a great opportunity to detect and further analyse the $\phi\pi^{+}\pi^{-}$ channel, with all its rich potential. On the other hand, it offers the possibility to tune trigger algorithms needed for PANDA at FAIR for open and hidden strangeness ($K^{\pm}, K_S, K_L, \phi$) in order to be able to select these signatures with a high efficiency as well as test and further develop the partial wave analysis software necessery to determine their properties from both GlueX and PANDA data.\\
Due to my experience regarding hardware, I see also a large potential to contribute to the DIRC detectors being developed for both experiments, which are key devices for $kaon/pion$ separation and thus are naturally related to the physics aimed for above.

\end{document}