\documentclass{article}
\RequirePackage[a4paper]{geometry}
\geometry{top=25mm,bottom=25mm,left=25mm,right=25mm,nohead,nofoot,includeheadfoot}
\pagestyle{empty}
\usepackage[utf8]{inputenc} % input encoding can be adjusted as needed
\usepackage{mathptmx,graphicx}
\begin{document}
\begin{center}
{\Large\bfseries Search for the Y(2175) in Photo-production at GlueX \par}
\vspace{3ex}
% {\bfseries Abdennacer Hamdi\par}
% {\footnotesize\itshape Institut für Kernphysik, J. W. Goethe-Universität, Max-von-Laue-Str. 1, 60438 Frankfurt am Main, Germany\par}
% \vspace{3ex}
{\bfseries Abdennacer Hamdi$^{1,2}$, Klaus Götzen$^{1}$, Frank Nerling$^{1,2}$, Klaus Peters$^{1,2}$ \par}
{\footnotesize\itshape
1. Institut für Kernphysik, J. W. Goethe-Universität, Max-von-Laue-Str. 1, 60438 Frankfurt am Main, Germany \par
2. GSI Helmholtzzentrum für Schwerionenforschung GmbH, Planckstraße 1, 64291 Darmstadt, Germany \par}
\vspace{3ex}
\end{center}
Quantum Chromodynamics is the theory that describes how hadrons are built from quarks and gluons via the strong 
interaction. Many predictions have been observed, but many others are still pending and under experimental 
investigation.
Of particular interest is how gluonic excitations give rise to exotic states. One class of such states are hybrid
mesons that are predicted by theoretical models and Lattice Quantum Chromodynamics calculations.
The $Y(2175)$, as observed in electron-positron experiments, is discussed to be strangeonium partner of
the $Y(4260)$, and thus a candidate for e.g. a hybrid meson or tetraquark state.
We present the status and plans to search for this state in photo-production at the GlueX experiment
in Jefferson Lab’s Hall D, which started physics data taking in 2016.
This work is supported by HGS-HIRe.

\setlength\parindent{0pt}\vspace{2ex}
%\textbf{References}

\footnotesize
%\hangindent=1.5em
\phantom{[1] Bernhard Ketzer, Proceedings of the Sixth International Conference on Quarks and Nuclear Physics (QNP2012), \textbf{arXiv:1208.5125v1} (2012).}

%\hangindent=1.5em
%[2] Gui-Jun Ding and Mu-Lin Yan, Phy. Lett.\textbf{B650}, 390 (2007).

\hangindent=1.5em
%[1] The BABAR Collaboration, B. Aubert, et al, Phys.Rev.\textbf{D74}, 091103 (2006).  \par
%\hspace{3ex} BES Collaboration, M. Ablikim, et al, Phys.Rev.Lett.\textbf{100}, 102003 (2008). \par
%\hspace{3ex} The Belle Collaboration, C. P. Shen, et al, Phys.Rev.\textbf{D80}, 031101 (2009).

%\hangindent=1.5em
%[4] BES Collaboration, M. Ablikim, et al, Phys.Rev.Lett.\textbf{100}, 102003 (2008).

%\hangindent=1.5em
%[5] The Belle Collaboration, C. P. Shen, et al, Phys.Rev.\textbf{D80}, 031101 (2009).

\end{document}