\section*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

First and foremost I would like to express my sincere gratitude to my advisor Professor Klaus Peters for the continuous support of my Ph.D study and related research, for his patience, motivation, and immense knowledge. His guidance helped me in all the time of my research project. I also appreciate all his contributions of time, ideas, and funding to make my Ph.D. experience productive and stimulating.
~\par Besides my supervisor, I would like to thank the rest of my thesis committee for their insightful comments and encouragement, but also for the important questions which rise a fruitful discussion, helping me to widen my research from various perspectives.
~\par My sincere thanks also goes to Dr. Frank Nerling, Dr. Klaus G\"otzen, and Dr. Ralf Kliemt, who provided me with many opportunities to discuss my results, offering their expertise, assistance, and patience. Without their precious support it would not be possible to conduct this research.
~\par I would also wish to express my gratitude to the GlueX colleagues for extended discussions and valuable suggestions which have contributed greatly to the improvement of the research project.
~\par I gratefully acknowledge the funding sources that made my Ph.D. work possible. I was funded by the Frankfurt Goethe University and GSI Helmholtz center. My work was also supported by the HGS-HIRe institute.
~\par I thank my fellow colleagues in for the stimulating discussions, for the sleepless nights we were working together before deadlines, and for all the fruitful exchange we have had in the last four years.
~\par Last but not the least, I would like to thank my family and friends for all their encouragements.

% \textit{Enfin je remercie \'egalement Mr. Alain FALVARD le directeur du LPC qui m'a permis de faire le stage au sein de son laboratoire.}