\phantomsection\addcontentsline{toc}{section}{References}
\begin{thebibliography}{ABC}	
    \bibitem[1]{1} K.A.Olive et al. (Particle Data Group). \emph{Particle Physics Booklet}. Chin. Phys. C, 38, 090001, 2014.
    \bibitem[2]{2} Fedor Bezrukov and Mikhail Shaposhnikov. \emph{Why should we care about the top quark Yukawa coupling?}. CERN, CH-1211 Genève 23, Switzerland, November 10, 2014. \url{http://arxiv.org/abs/1411.1923v1}
    \bibitem[3]{3} Ryo Yonamine, Katsumasa Ikematsu, Tomohiko Tanabe, Keisuke Fujii, Yuichiro Kiyo, Yukinari Sumino and Hiroshi Yokoya. \emph{Measuring the top Yukawa coupling at the ILC at $\sqrt{s}$ = 500 GeV}. 2011. \url{http://arxiv.org/abs/1104.5132v1}
      \bibitem[4]{4} M. Battaglia, T. Barklow, M. E. Peskin, Y. Okada, S. Yamashita and, P. Zerwas.  \emph{Physics Benchmarks for the ILC Detectors}. 2006. \url{http://arxiv.org/abs/hep-ex/0603010v1}.
    \bibitem[5]{5} The International Linear Collider. \emph{Technical Design Report Volume 2: Physics} , 2013.
    \bibitem[6]{6} The International Linear Collider. \emph{Technical Design Report Volume 4: Detectors} , 2013.
    \bibitem[7]{7}  Alexey PETRUKHIN, \emph{Energy measurement with the SDHCAL prototype}. CALICE Collaboration, IPNL/CNRS, France, 2014. \url{http://arxiv.org/abs/1406.7111v1}.
    \bibitem[8]{8} Rémi Été. \emph{Séparation de gerbes hadroniques proches dans le Calorimètre Hadronique Semi-Digital SDHCAL pour ILC }. Rapport de Stage de Master II Physique Fondamentale et Astrophysique, Institut de Physique Nucléaire de Lyon, Université Claude Bernard Lyon 1. \url{http://rete.github.io/reports/M2.pdf}.
\end{thebibliography}
