\documentclass[11pt]{letter}
 \usepackage[utf8]{inputenc} % un package
 \usepackage[T1]{fontenc} % un second package
%\usepackage[latin1]{inputenc}
 \usepackage[english]{babel} % un troisième package
 \usepackage{textcomp}
 \usepackage{ifpdf}
\ifpdf
 \usepackage[pdftex]{graphicx}
 \else
 \usepackage[dvips]{graphicx}\fi
\pagestyle{empty}
\usepackage[scale=0.88]{geometry}
 \setlength{\parindent}{1em}
\addtolength{\parskip}{0.5pt}
\renewcommand{\ttdefault}{pcr}
 \begin{document}
 \sffamily
 \hfill
 %start
 \begin{flushleft}
 {\bfseries Abdennacer Hamdi}\\[.35ex]
 \small\itshape
 Herzogstra{\ss}e 13 \\
 60528 Frankfurt am Main \\
 Germany \\[.35ex]
 (+49) 01781043207 \\
 nacer\_h@outlook.com
 \end{flushleft}
 %
 \begin{flushleft}
 To {\bfseries Frau Lena Rokahr}\\[.35ex]
 \small\itshape
 Senacor Technologies AG \\
 Litfaßplatz 2 \\
 10178 Berlin
 \end{flushleft}
 %
 \hfill
 %
 \begin{flushleft}
 Frankfurt am Main, \today \\
 
 \end{flushleft}
 %
% \textit{Subject:} Application for postdoctoral Associate position in nuclear physics.\\
\par Dear Frau Lena Rokahr,
%Content of the letter
~\par It is with great pleasure that I am writing to you to express my interest in applying for the new Physiker als Berater position to work together with the Senacor Technologies AG group. This position appeals to me because of my strong interest in consulting and software development, in addition to using the knowledge I have gained through my six years of experience in the field of data analysis, software development, as well as team and public communication.
~\par I have been seeking just such an opportunity as this, it is clear to me that Senacor is genuinely devoted to the development of high quality IT and consulting services and to the advancement of professional career. I will have the opportunity to work and learn from the best and the privilege to work in an international environment. I believe I can contribute to that mission through my passion for consulting an software development, my education and background would be a good match for your requirements.
~\par I mention that I am currently finishing my Ph.D project at the Goethe University of Frankfurt, where I analyze big data for an international collaboration. My job revolve around collecting, organizing, and analyzing data by developing statistical methods and new technics, as well as interpreting and communicating the results in international conferences. I had also the opportunity to guide master students during laboratory practical manipulations. During my master in France, I have worked as a sale agent in a retail company, where I learned to speak in a friendly way to customers, listening to their needs and helping communicate options for them. All these challenges have strengthened my skills in data analysis, software/hardware development, and gained experience working with different interdisciplinary teams.
~\par I am eager to talk with you about the proposed position and your company this would offer me the possibility of receiving the complete picture. I thank you for the opportunity to submit this application for your consideration. Please contact me if there is anything else I need to provide. I look forward to hearing from you in the near future. Please find enclosed my CV to this application.

\noindent Yours sincerely,

\begin{flushleft}
 {\bfseries Abdennacer Hamdi}
 \end{flushleft}
 \vfill
 \end{document}